Assessing the Replicability of Psychological Science Through Pedagogy

### 2016-07-08 paper/paper.Rmd
paper

```{r global_options, include=FALSE}
rm(list=ls())
library(knitr)
knitr::opts_chunk$set(fig.width=6, fig.height=5, fig.crop = FALSE, 
                      fig.path='figs/', echo=FALSE, warning = FALSE, 
                      cache=TRUE, message = FALSE, sanitize = TRUE)
library(readr)
library(dplyr)
library(xtable)
library(readr)
library(tidyr)
library(ggplot2)
library(BayesFactor)
#devtools::install_github("langcog/langcog")
library(langcog)
```

@@

ggplot(tstatDF, aes(x = origBF, y = repBF)) +
  geom_point(alpha = .8, aes(size = t_ratio, 
                             col = replicated_TA_factor)) +
  geom_abline(slope = 1, lty = 2) + 
  geom_smooth(method = "lm", se=FALSE) + 
  xlab("Original Bayes Factor") + 
  ylab("Replication Bayes Factor") + 
  scale_x_log10(limits = c(10**-1.75, 10**11), 
                breaks = c(1/10, 1/3, 3, 10, 100),
                labels = c("1/10", "1/3", "3", "10")) +
  scale_y_log10(limits = c(10**-1.75, 10**11),
                breaks = c(1/10, 1/3, 3, 10, 100),
                labels = c("1/10", "1/3", "3", "10")) + 
  scale_size_continuous(name = "Ratio of replication to original t value") + 
  scale_color_solarized(name = "Subjective replication rating") + 
  theme_bw() +
  theme(legend.position="bottom")

  # xlim(-2, 30) +
  # ylim(-2, 30) +
  # geom_hline(aes(yintercept = 10), linetype = 2)+
  # geom_hline(aes(yintercept = 3), linetype = 2)+
  # geom_hline(aes(yintercept = 1/3), linetype = 2)+
  # geom_hline(aes(yintercept = 1/10), linetype = 2)+
  # geom_vline(aes(xintercept = 10), linetype = 2)+
  # geom_vline(aes(xintercept = 3), linetype = 2)+
  # geom_vline(aes(xintercept = 1/3), linetype = 2)+
  # geom_vline(aes(xintercept = 1/10), linetype = 2) +
```

@@

## Exploratory analysis

>>>>

```{r global_options, include=FALSE}
rm(list=ls())
library(knitr)
knitr::opts_chunk$set(fig.width=6, fig.height=5, fig.crop = FALSE, 
                      fig.path='figs/', echo=FALSE, warning = FALSE, 
                      cache=FALSE, message = FALSE, sanitize = TRUE)
library(readr)
library(dplyr)
library(xtable)
library(readr)
library(tidyr)
library(ggplot2)
library(BayesFactor)
library(ggrepel)
#devtools::install_github("langcog/langcog")
library(langcog)
```

@@

tstatDF$origBF[7] <- 1e+11

ggplot(tstatDF, aes(x = origBF, y = repBF)) +
  geom_point(alpha = .8, aes(size = t_ratio, 
                             col = replicated_TA_factor)) +
  geom_abline(slope = 1, lty = 2) + 
  geom_smooth(method = "lm", se=FALSE) + 
  geom_text_repel(aes(label = first_author_name), size = 3) + 
  xlab("Original Bayes Factor") + 
  ylab("Replication Bayes Factor") + 
  scale_x_log10(limits = c(10**-1.75, 10**11), 
                breaks = c(1/10, 1/3, 3, 10, 100, 100000),
                labels = c("1/10", "1/3", "3", "10","100", "1,000,000")) +
  scale_y_log10(limits = c(10**-1.75, 10**11),
                breaks = c(1/10, 1/3, 3, 10, 100, 100000),
                labels = c("1/10", "1/3", "3", "10","100", "1,000,000")) + 
  scale_size_continuous(name = "Ratio of replication to original t value") + 
  scale_color_solarized(name = "Subjective replication rating") + 
  theme_bw() +
  theme(legend.position="bottom")
```

@@
